Interim Report WV

### 2015-03-27 tussentijdsverslag/tussentijdsverslag.tex
interim report
antenna

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Tussentijds verslag WV}
\author{Ward  Xavier}
\date{March 2015}

@@

\section{Update}

\section{Voorlopige resultaten}

\section{Vragen}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}

\title{Interim Report WV}
\author{Ward  Xavier}
\date{March 2015}

@@

\section{Update}
Due neverending problems with over-the-air-deployment we decided to stop researching using Looci. We are now using just Contiki on the motes. We deploy components with the flasher.
\section{Interim Results}
\subsection{Antenna}
We used the data provided at \url{http://people.cs.kuleuven.be/~wilfried.daniels/energy/results3.html} and used it to derive the energy cost per byte:

\subsection{RAM}

\subsection{Flash}
As discussed with Klaas, we will only research this option when we have time.

\subsection{Interim Conclusion}
\section{Questions}
